\Large {\bf Flow-guided Analysis of System-level Post-silicon Traces Under Limited Observability}

### 2015-09-05 paper.tex
hyperref
Test commit
Changed to ISQED format and also changed title

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{mybeamer}
\usepackage{draftwatermark}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Flow-Directed Trace Analysis for Post-Silicon Validation}

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Hao Zheng, Yuting Cao}
\IEEEauthorblockA{Computer Science and Engineering\\
University of South Florida\\
Tampa, Florida 33620}
\and
\IEEEauthorblockN{Sandip Ray, Jin Yang}
\IEEEauthorblockA{Strategic CAD Labs\\
Intel Corporation\\
Portland, Oregon
}}

@@

% make the title area
\maketitle

@@

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

@@

For this model, we consider the flow specification describing the cache coherence protocol supported in GEM5 that is used to build the model in Fig~\ref{SoC}.  This specification consists of two flows, one for cache coherent read requests and one for  cache coherent write requests, from CPUs.  Two such flows describe the cache coherent protocol for each CPU.  As there are two CPUs in this model, there are actually four such flows considered for this model.  
%More detailed information about the flow specification is explained in the following section.

%found at \red{github???}

>>>>

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.
\usepackage{pifont}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{mybeamer}
\usepackage{draftwatermark}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}

@@

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{\Large {\bf Flow-guided Analysis of System-level Post-silicon
  Traces Under Limited Observability}}

\author{\large Hao Zheng$^1$, Yuting Cao$^1$, Sandip Ray$^2$, Jin Yang$^2$ \\
$^1$Dept. of Computer Science and Engg., University of South Florida, Tampa, Fl 33620. USA. \\
$^2$Strategic CAD Labs, Intel Corporation, Hillsboro, OR 97124.  USA.}
\maketitle

%% % author names and affiliations
%% % use a multiple column layout for up to three different
%% % affiliations
%% \author{\IEEEauthorblockN{Hao Zheng, Yuting Cao}
%% \IEEEauthorblockA{Computer Science and Engineering\\
%% University of South Florida\\
%% Tampa, Florida 33620}
%% \and
%% \IEEEauthorblockN{Sandip Ray, Jin Yang}
%% \IEEEauthorblockA{Strategic CAD Labs\\
%% Intel Corporation\\
%% Portland, Oregon
%% }}

@@

% make the title area
%\maketitle

@@

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
% \IEEEpeermaketitle

@@

For this model, we consider the flow specification describing the cache coherence protocol supported in GEM5 that is used to build the model in Fig~\ref{SoC}.  This specification consists of two flows, one for cache coherent read requests and one for  cache coherent write requests, from CPUs.  Two such flows describe the cache coherent protocol for each CPU.  As there are two CPUs in this model, there are actually four such flows considered for this model.  More detailed information about the flow specification can be found at \url{https://github.com/cao2/paper/blob/master/Flow\%20Specification.pdf}
